### 2016-06-13 paper-arxiv-v3/sec-mcsamples.tex
revised paper

Background samples are generated at leading order
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
we use as
factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
%
We account for all relevant background
processes that can mimic the
 $hh\to 4b$ signal process.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ production, and top quark pair
production.
%
The latter is restricted to the fully hadronic final state,
since 
leptonic decays of top quarks can be removed by requiring
a lepton veto.
%
Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and are therefore not included in the present analysis.
%

>>>>

Background samples are generated at leading order
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
we use as
factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
%
We account for all relevant background
processes that can mimic the
 $hh\to 4b$ signal process.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ production, and top quark pair
production.
%
The latter is restricted to the fully hadronic final state,
since 
leptonic decays of top quarks can be removed by requiring
a lepton veto.
%
Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$ (see Appendix~\ref{app:singlehiggs})
along with electroweak backgrounds {\it e.g} $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the
QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and are therefore not included in the present analysis.

### 2016-06-13 paper-arxiv-v3/sec-mva.tex
revised paper

From Table~\ref{table:cutflowMVA} we see that
following the application of the MVA, 
the signal significance in the boosted category increases
from 0.5 to 2.7, with $S/B$ increasing from $0.06\%$ to $3\%$.
%
For the intermediate and resolved categories, $S/\sqrt{B}$
increases from 0.4 to 2.3 and 1.9 respectively, with
the signal over background ratio raising from
$0.05\%$ and $0.01\%$ to 4\% and 1\%.
%
Combining the three categories, taking into
account all background components, we obtain the overall signal
significance:
\be
\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
\ee
%
The signal significance for
$\mathcal{L}=3$ ab$^{-1}$
is thus
well above the threshold for the observation of Higgs
pair production.
%
However, given that the HL-LHC will be a high-PU environment,
which will affect the description of the various
kinematic distributions used as input to the MVA,
it is essential to quantify the robustness of these
results
in a realistic environment including the effects of
significant PU.

@@

>>>>

From Table~\ref{table:cutflowMVA} we see that
following the application of the MVA, 
the signal significance in the boosted category increases
from 0.5 to 2.7, with $S/B$ increasing from $0.06\%$ to $3\%$.
%
For the intermediate and resolved categories, $S/\sqrt{B}$
increases from 0.4 to 2.3 and 1.9 respectively, with
the signal over background ratio raising from
$0.05\%$ and $0.01\%$ to 4\% and 1\%.
%
Combining the three categories, taking into
account all background components, we obtain the overall signal
significance:
\be
\label{eq:soverb}
\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
\ee
%
The signal significance for
$\mathcal{L}=3$ ab$^{-1}$
is thus
well above the threshold for the observation of Higgs
pair production.
%
However, given that the HL-LHC will be a high-PU environment,
which will affect the description of the various
kinematic distributions used as input to the MVA,
it is essential to quantify the robustness of these
results
in a realistic environment including the effects of
significant PU.

@@

A particularly challenging aspect of our analysis is the modeling of the $2b2j$ and $4j$ background,
specially of the latter, which require extremely large MC samples.
%
In the analysis reported here, out of the original 3M $4j$ generated events, only around 100
survive the analysis cuts, and thus
these low statistics have associated a potentially large uncertainty
in the calculation of the post-MVA $4j$ cross-section.
%
On the other hand, since the $4j$ cross-sections
are always quite smaller than the sum of the $4b$ of the $2b2j$ components,
this low statistics should not modify qualitatively our conclusions above.
%
To verify explicitly this expectation, and obtain a more
robust estimate of the  background cross-section from mis-identified jets,
we have increased by a factor 10 the size of the $2b2j$ and $4j$
background samples, up to a total of 30M each.
%
Processing these events though our analysis, including retraining the MVA, we find
$(S/\sqrt{B})_{\rm tot}=3.9$, consistent with Eq.~(\ref{eq:soverb}), indicating that the low
statistics of the $4j$ background is not a limiting factor.
